Quantifying Roughness in SAR Imagery with the Rényi Entropy

### 2025-05-20 Text/Articles/RENYI_ENTROPY_SAR_2025/Reviews/Responses-Associate-Editor.tex

\documentclass[11pt]{report}

\usepackage[pdftex]{geometry}
\geometry{a4paper,left=2.8cm,right=2.8cm,top=1.5cm,bottom=1.5cm,twoside}

\usepackage{amssymb}
\usepackage{enumerate}
\usepackage{graphicx}
	\graphicspath{./Comments/}
\usepackage[many]{tcolorbox}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{subfigure}
\usepackage{bm,bbm}
\usepackage{float}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\newtcolorbox{reviewbox}[1]{
colback = white!5!white,
colframe = purple!75!black,
fonttitle=\bfseries,
title=#1
}

\newtcolorbox{responsebox}[1]{
	colback = white!5!white,
	colframe = white!75!black,
	fonttitle=\bfseries,
	title=#1
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{center}
\large{\textbf{Response Letter to Associate Editor}}

\vglue 0.3cm

\huge{ Quantifying Roughness in SAR Imagery with the Rényi Entropy\\ (GRSL-00722-2025)}
\end{center}

%\authors
\begin{center}
\textbf{Janeth Alpala,   Abraao D.\ C.\ Nascimento, Alejandro C.\ Frery }
\end{center}

\date{\today}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{2cm}
\noindent Dear Editors
\bigskip

\noindent We are grateful to the reviewers for the valuable comments and the time spent on checking our manuscript. 
We have addressed their comments towards improving the paper contents and presentation. 
Below we detail the changes and updates incorporated into the manuscript in this round of review.

\medskip

%-------------------------------------
\begin{reviewbox}{Comment 1}
This manuscript proposes a statistically grounded method for quantifying roughness in SAR imagery using a non-parametric estimator of Rényi entropy, refined via bootstrap correction, and developed into a hypothesis test that distinguishes fully developed speckle and heterogeneous clutter. The paper is technically sound and well-presented. However, the following comments should be carefully addressed in the revised version to enhance clarity, applicability, and completeness:

1. While the paper is generally well-written and structured, several mathematical expressions—particularly Equations (5) and (8)—may be difficult to interpret for practitioners or applied researchers. The authors are encouraged to provide more intuitive explanations or illustrative interpretations alongside the formulas.
\end{reviewbox}

\begin{responsebox}{Response}

We have

\begin{quote}
	\textcolor{blue}{text  }
\end{quote}

\end{responsebox}

\begin{reviewbox}{Comment 2}
2. The current methodology assumes that the number of looks, L, is known a priori. In practice, this parameter may be unknown or inaccurately estimated from SAR metadata. The authors should discuss the sensitivity of the proposed test to variations or inaccuracies in L, and optionally suggest techniques for estimating L directly from the data or include robustness analysis. 
\end{reviewbox}

\begin{responsebox}{Response}

We have clarified that
\begin{quote}
	\textcolor{blue}{
		In order to clarify the }

\end{quote}

\end{responsebox}

\begin{reviewbox}{Comment 3}
3. Figures (Figs. 6–8) are informative but could benefit from quantitative evaluation. Add comparative metrics beyond visual comparison.
\end{reviewbox}

\begin{responsebox}{Response}

We include

\begin{quote}
	\textcolor{blue}{
	text
}
\end{quote}

\end{responsebox}

\begin{reviewbox}{Comment 4}
The manuscript convincingly shows that Rényi-based entropy measures offer advantages over classical Shannon entropy for heterogeneity detection. However, no comparisons are made to machine learning-based SAR classifiers or segmentation models, which are now widely adopted. Justification is required.
\end{reviewbox}
\begin{responsebox}{Response}
We have clarified that
\begin{quote}
	\textcolor{blue}{
		text
}
\end{quote}

\end{responsebox}

\end{document}

### 2025-05-20 Text/Articles/RENYI_ENTROPY_SAR_2025/Reviews/Responses-Reviewer1.tex

\vspace{2cm}
\noindent Dear Editors
\bigskip

\noindent We are grateful to the reviewers for the valuable comments and the time spent on checking our manuscript. 
We have addressed their comments towards improving the paper contents and presentation. 
Below we detail the changes and updates incorporated into the manuscript in this round of review.

\medskip

%-------------------------------------
\begin{reviewbox}{Comment 1}
1. The manuscript uses Rényi Entropy to estimate the surface roughness using SAR intensity data. However, the novelty aspect is not clear to this reviewer. Is this the sampling technique for the non-parametric estimation? The non-parametric estimation is already existing in the literature.

\end{reviewbox}

\begin{responsebox}{Response}
We have 
\begin{quote}
	\textcolor{blue}{ text}
\end{quote}
\end{responsebox}

\vspace{2em}
\begin{reviewbox}{Comment 2}
2. The methodology is mostly indicates the heterogeneity in a SAR image. The terminology "Roughness" generally refers to the surface roughness irrespective of the landcover classes. However, the proposed technique includes everything which are existing within a resolution. Therefore, in the title of the manuscript, the "Roughness" can be changed to "Heterogeneity".
\end{reviewbox}

@@

\begin{responsebox}{Response}

We change to the new title..
\begin{quote}
	\textcolor{blue}{
	Quantifying Heterogeneity in SAR Imagery with the Rényi Entropy
}
\end{quote}
\end{responsebox}

\vspace{2em}
\begin{reviewbox}{Comment 3}
3. Why the p-values are very high over the areas which have the dominant surface scattering? Should it not be low if the proposed technique is estimating the entropy precisely? It looks like the proposed method better estimates over the heterogeneous areas as compared to homogeneous areas.
\end{reviewbox}
\begin{responsebox}{Response}
	text
\end{responsebox}

\vspace{2em}
\begin{reviewbox}{Comment 4}
4. How is the dependence of the proposed technique on the additive and multiplicative noises which remains in the SAR data?
\end{reviewbox}
\begin{responsebox}{Response}

@@

\end{responsebox}

\vspace{2em}
\begin{reviewbox}{Comment 5}
5. Fig 6, 7 and 8 show the detection of heterogeneous areas. However, a statistical measure indicating the detection performance is absent.
\end{reviewbox}
\begin{responsebox}{Response}

We have clarified  that
\begin{quote}
	\textcolor{blue}{text}
\end{quote}
\end{responsebox}

\vspace{2em}
\begin{reviewbox}{Comment 6}
6. The color bars and the font size of the texts needs to be improved so that it can be clearly visible.
\end{reviewbox}
\begin{responsebox}{Response}

We added

@@

\end{responsebox}

\vspace{2em}
\begin{reviewbox}{Comment 7}
7. Why the authors are focusing on the low MSE, not the low bias while selecting the value of lambda?
\end{reviewbox}

\begin{responsebox}{Response}
text
\end{responsebox}

\vspace{2em}
\begin{reviewbox}{Comment 7}
8. "We aim to determine the optimal order λ for the Rényi entropy estimator for a sample size n=49" From where these 49 samples are taken?
\end{reviewbox}

\begin{responsebox}{Response}
text
\end{responsebox}
\end{document}

### 2025-05-20 Text/Articles/RENYI_ENTROPY_SAR_2025/Reviews/Responses-Reviewer2.tex

\vspace{2cm}
\noindent Dear Editors
\bigskip

\noindent We are grateful to the reviewers for the valuable comments and the time spent on checking our manuscript. 
We have addressed their comments towards improving the paper contents and presentation. 
Below we detail the changes and updates incorporated into the manuscript in this round of review.

\medskip

%-------------------------------------
\begin{reviewbox}{Comment 1}
1. The language needs further improvement and should be reviewed by a language expert.
\end{reviewbox}

\begin{responsebox}{Response}
Text

\begin{reviewbox}{Comment 2}
2. The scientific content of the article is weak and requires further expansion.
\end{reviewbox}

@@

\begin{responsebox}{Response}

Text

\end{responsebox}

\begin{reviewbox}{Comment 3}
 3. I did not observe any comparison of the authors' work's novelty index with the latest articles published in the field for the current years.
\end{reviewbox}

Text

\end{responsebox}
\begin{reviewbox}{Comment 4}
4. Conclusion requires redrafting.
\end{reviewbox}
\begin{responsebox}{Response}
Text

### 2025-05-20 Text/Articles/RENYI_ENTROPY_SAR_2025/R1-Renyi-entropy-sar.qmd
new R1-version qmd and new Figures-R1

---
title: Quantifying Roughness in SAR Imagery with the Rényi Entropy
format:
  ieee-pdf:
    pdf-engine: pdflatex # xelatex
    keep-tex: true  
    classoption: lettersize
    tex-author-no-affiliation: true
    #conference: true # comment this line to use journal
    #journaltype: conference # comment this line to use journal
    fig-cap-location: bottom # to crossref figure
    link-citations: true
    colorlinks: true
    linkcolor: black # equations
    citecolor: black # cites
    urlcolor: black
  #ieee-html: default
author:
  - name: Janeth Alpala
    email: janeth.alpala@ufpe.br
    orcid: 0000-0002-0265-6236
  - name: Abraão D.&nbsp;C.&nbsp;Nascimento
    affiliations:
      - name: Universidade Federal de Pernambuco
        department: Departamento de Estatística
        city: Recife
        country: Brazil
        postal-code: 50670-901
    email: abraao@de.ufpe.br
    orcid: 0000-0003-2673-219X
  - name: Alejandro C.&nbsp;Frery
    affiliations:
      - name: Victoria University of Wellington
        department: School of Mathematics and Statistics
        city: Wellington
        country: New Zealand
        postal-code: 6140
    orcid: 0000-0002-8002-5341
    email: alejandro.frery@vuw.ac.nz
    membership: Fellow, IEEE
    attributes:
      corresponding: true
    note: |
      Janeth Alpala and Abraão D. C. Nascimento are with the Departamento de Estatística, Universidade Federal de Pernambuco, Recife, 50670-901 PE, Brazil (e-mails: janeth.alpala@ufpe.br, abraao@de.ufpe.br).

@@

knitr::opts_chunk$set(echo = FALSE, cache = TRUE)

@@

@fig-plot illustrates this convergence by showing $H_\lambda(\mathcal{G}^0_I)$  as a function of $\mu$ for different values of $\alpha$. As $\alpha$ decreases, the curves approach $H_\lambda(\Gamma_{\text{SAR}})$ (solid black line). This confirms that $\Gamma_{\text{SAR}}$ is a limiting case of $\mathcal{G}^0_I$.
<!-- ACF Have you checked if it is possible to state the difference between \label{eq-HGI0} and \label{eq-HGammaSAR}? At the end of the day, that is what we want to assess. -->
<!-- Corrected -->
```{r fig-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="45%",  fig.pos="hbt", fig.cap="$H_{\\lambda}(\\mathcal{G}^0_I)$ converges to the $H_{\\lambda}(\\Gamma_{\\text{SAR}})$ when $\\alpha\\to-\\infty$, with $L=8$ and $\\lambda=0.8$.", fig.width=4.5, fig.height=3.5}

@@

We found that the optimal value for $L > 1$ is $\lambda = 0.9$, as it minimizes the MSE while maintaining a low bias.
However, for $L = 1$, the optimal $\lambda$ tends to be higher, and we chose $\lambda = 3$ to achieve good results. 
@fig-plotf illustrates the case for $L = 5$.
```{r fig-plotf, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="42%",  fig.pos="hbt", fig.cap="Bias and MSE as a function of $\\lambda$, with $n=49$, $L=5$.", fig.width=7, fig.height=4.5}

@@

A Monte Carlo study with $1000$ replications for each sample size $n \in \{9, 25, 49, 81, 121\}$ from the $\Gamma_{\text{SAR}}$ ($\mu=1, L=5$) confirms that for $\lambda=0.9$, the bootstrap-corrected estimator $\widetilde{H}_{\lambda}$ ($B=200$) reduces both bias and MSE compared to the original $\widehat{H}_{\lambda}$, with significant improvements for small sample sizes, as shown in&nbsp;@fig-Plot_bias_msef3.

@@

```{r fig-Plot_bias_msef3, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="42%", fig.pos="hbt",  fig.cap="Bias and MSE of the Rényi entropy estimators for $\\Gamma_{\\text{SAR}}$.", fig.width=7, fig.height=5}

@@

Assume we have an estimator $\widetilde{H}_{\lambda}$ for the Rényi entropy of an arbitrary model. For testing&nbsp;\eqref{eq:hypothesis_test}, this estimator is expected to be close to the theoretical expression given in Equation&nbsp;\eqref{eq-HGammaSAR}. 
Since $L\geq1$ is known, we define the test statistic as follows:
\begin{multline}
\label{eq-test}
S_{\widetilde{H}_{\lambda}}(\bm{Z}; L) = \widetilde{H}_{\lambda} - \bigl\{\ln \widehat{\mu} - \ln L + \frac{1}{1-\lambda}
\bigl[-\lambda\,\ln\Gamma(L) \\ 
+ \ln\Gamma\bigl(\lambda(L-1)+1\bigr)  
- \bigl(\lambda(L-1)+1\bigr)\,\ln\lambda
\bigr]\bigr\},
\end{multline}
where $\widehat{\mu}={n}^{-1}\sum_{i=1}^n Z_{i}$ is the sample mean.
This test statistic should be close to zero when the null hypothesis holds.
@fig-density_entropyR shows the empirical density of $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$, based on $10^4$ replications of the $\Gamma_{\text{SAR}}$ model for each sample size $n \in \{49,81, 121\}$ with $\lambda=0.9$ and $L \in \{5,18\}$.
<!-- ACF 10^4 replications of samples of size?   -->
<!-- Corrected -->
```{r Simulated_densityR, echo=FALSE, message=FALSE}
set.seed(1234567890, kind = "Mersenne-Twister")

@@

```{r fig-density_entropyR, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="47%", fig.pos="hbt",  fig.cap="Empirical densities of $S_{\\widetilde{H}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$.", fig.width=9, fig.height=4.0}

@@

The standardized test statistic 
$\varepsilon = ({S_{\widetilde{H}_{\lambda}}(\bm{Z}; L) - \hat{\mu}_S})/{\hat{\sigma}_S}$ is asymptotically standard normal distributed,
where $\hat{\mu}_S$ and $\hat{\sigma}_S$ are the empirical mean and standard deviation of $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$, obtained by Monte Carlo simulations under the null hypothesis. 
Thus, the $p$-values are calculated as $2\Phi(-|\varepsilon|)$,
where $\Phi(\cdot)$ is the cumulative distribution function of the standard normal distribution.
@fig-density_entropyR_standardized0 shows smoothed histograms of standardized test statistics.

@@

```{r fig-density_entropyR_standardized0, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="35%", fig.pos="hbt", fig.cap="Standardized empirical densities of $S_{\\widetilde{H}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$.", fig.width=4, fig.height=2.5}

@@

The Rényi entropy-based test demonstrated greater sensitivity in detecting textural variations than the Shannon-based test due to the flexibility provided by the parameter $\lambda$, as observed in the binary maps in Figs.&nbsp;\ref{fig:london-c},&nbsp;\ref{fig:munich-c}, and&nbsp;\ref{fig:dublin-c}.
<!-- ACF Where is the Shannon-based approach shown? -->
<!-- JA: The results of the Shannon-based approach can be observed in the corresponding binary maps. -->
```{=latex}
\begin{figure*}[hbt]
    \centering
    \begin{subfigure}{0.17\textwidth}
        \includegraphics[width=\linewidth]{./Figures/london_2000.png}
        \caption{ SAR image}
        \label{fig:london-a}
    \end{subfigure}
    \begin{subfigure}{0.22\textwidth}
        \includegraphics[width=\linewidth]{./Figures/H_pvalue_london_renyi.png}
        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\lambda}}}$}
        \label{fig:london-b}
    \end{subfigure}
    \begin{subfigure}{0.17\textwidth}
        \includegraphics[width=\linewidth]{./Figures/H_005_london_renyi_L1_.png}
        \caption{Binary map for $\small{S_{\widetilde{H}_{\lambda}}}$}
        \label{fig:london-c}
    \end{subfigure}
    \begin{subfigure}{0.22\textwidth}
        \includegraphics[width=\linewidth]{./Figures/H_pvalue_london_Shannon_c1.png}
        \caption{$p$-value map for $\tiny{S_{\widetilde{H}_{\text{AO}}}}$ }
        \label{fig:london-d}
    \end{subfigure}
    \begin{subfigure}{0.17\textwidth}
        \includegraphics[width=\linewidth]{./Figures/H_005_london_shannon.png}
        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
        \label{fig:london-e}
    \end{subfigure}
    \caption{Detection of heterogeneous areas in a SAR image over London, UK: comparison with the tests $\small{S_{\widetilde{H}_{\lambda}}}$ and $\small{S_{\widetilde{H}_{\text{AO}}}}$.  }
    \label{fig:london}
\end{figure*}

@@

```{=latex}
\begin{figure*}[hbt]
    \centering
    \begin{subfigure}{0.17\textwidth}
        \includegraphics[width=\linewidth]{./Figures/munich_1024_2.png}
        \caption{SAR image}
        \label{fig:munich-a}
    \end{subfigure}
    \begin{subfigure}{0.23\textwidth}
        \includegraphics[width=\linewidth]{./Figures/H_pvalue_muni_renyi.png}
        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\lambda}}}$}
        \label{fig:munich-b}
    \end{subfigure}
    \begin{subfigure}{0.16\textwidth}
        \includegraphics[width=\linewidth]{./Figures/H_005_munich_renyi.png}
        \caption{Binary map for $\small{S_{\widetilde{H}_{\lambda}}}$}
        \label{fig:munich-c}
    \end{subfigure}
    \begin{subfigure}{0.23\textwidth}
        \includegraphics[width=\linewidth]{./Figures/H_pvalue_muni_Shan22.png}
        \caption{$p$-value map for $S_{\widetilde{H}_{\text{AO}}}$}
        \label{fig:munich-d}
    \end{subfigure}
    \begin{subfigure}{0.16\textwidth}
        \includegraphics[width=\linewidth]{./Figures/H_005_munich_sh_AO_L12.png}
        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
        \label{fig:munich-e}
    \end{subfigure}
    \caption{Detection of heterogeneous areas in a SAR image over Munich, Germany: comparison with the tests $\small{S_{\widetilde{H}_{\lambda}}}$ and $\small{S_{\widetilde{H}_{\text{AO}}}}$.}
    \label{fig:munich}
\end{figure*}

```{=latex}
\begin{figure*}[hbt]
    \centering
    \begin{subfigure}{0.16\textwidth}
        \includegraphics[width=\linewidth]{./Figures/dublin_1100_hh.png}
        \caption{SAR image}
        \label{fig:dublin-a}
    \end{subfigure}
    \begin{subfigure}{0.22\textwidth}
        \includegraphics[width=\linewidth]{./Figures/dublin_renyi_09_w7_b100.png}
        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\lambda}}}$}
        \label{fig:dublin-b}
    \end{subfigure}
    \begin{subfigure}{0.16\textwidth}
        \includegraphics[width=\linewidth]{./Figures/H_005_dublin_renyi_09_w7_b100.png}
        \caption{Binary map for $\small{S_{\widetilde{H}_{\lambda}}}$}
        \label{fig:dublin-c}
    \end{subfigure}
    \begin{subfigure}{0.22\textwidth}
        \includegraphics[width=\linewidth]{./Figures/AO_w7_L16_b100.png}
        \caption{$p$-value map for $S_{\widetilde{H}_{\text{AO}}}$}
        \label{fig:dublin-d}
    \end{subfigure}
    \begin{subfigure}{0.16\textwidth}
        \includegraphics[width=\linewidth]{./Figures/H_005_AO_w7_L16_b100.png}
        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
        \label{fig:dublin-e}
    \end{subfigure}
   \caption{Detection of heterogeneous areas in a SAR image over Dublin Port, Ireland: comparison with the tests $\small{S_{\widetilde{H}_{\lambda}}}$ and $\small{S_{\widetilde{H}_{\text{AO}}}}$.}

>>>>

---
title: Quantifying Roughness in SAR Imagery with the Rényi Entropy
format:
  ieee-pdf:
    pdf-engine: pdflatex # xelatex
    fig-dir: "Figures-R1"
    keep-tex: true  
    classoption: lettersize
    tex-author-no-affiliation: true
    #conference: true # comment this line to use journal
    #journaltype: conference # comment this line to use journal
    fig-cap-location: bottom # to crossref figure
    link-citations: true
    colorlinks: true
    linkcolor: black # equations
    citecolor: black # cites
    urlcolor: black
  #ieee-html: default
author:
  - name: Janeth Alpala
    email: janeth.alpala@ufpe.br
    orcid: 0000-0002-0265-6236
  - name: Abraão D.&nbsp;C.&nbsp;Nascimento
    affiliations:
      - name: Universidade Federal de Pernambuco
        department: Departamento de Estatística
        city: Recife
        country: Brazil
        postal-code: 50670-901
    email: abraao@de.ufpe.br
    orcid: 0000-0003-2673-219X
  - name: Alejandro C.&nbsp;Frery
    affiliations:
      - name: Victoria University of Wellington
        department: School of Mathematics and Statistics
        city: Wellington
        country: New Zealand
        postal-code: 6140
    orcid: 0000-0002-8002-5341
    email: alejandro.frery@vuw.ac.nz
    membership: Fellow, IEEE
    attributes:
      corresponding: true
    note: |
      Janeth Alpala and Abraão D. C. Nascimento are with the Departamento de Estatística, Universidade Federal de Pernambuco, Recife, 50670-901 PE, Brazil (e-mails: janeth.alpala@ufpe.br, abraao@de.ufpe.br).

@@

#knitr::opts_chunk$set(echo = FALSE, cache = TRUE)
knitr::opts_chunk$set(
  echo = FALSE,
  cache = TRUE,
  fig.path = "Figures-R1/"
) # unique path to save all code-generated and external figures

@@

@fig-convergence illustrates this convergence by showing $H_\lambda(\mathcal{G}^0_I)$  as a function of $\mu$ for different values of $\alpha$. As $\alpha$ decreases, the curves approach $H_\lambda(\Gamma_{\text{SAR}})$ (solid black line). This confirms that $\Gamma_{\text{SAR}}$ is a limiting case of $\mathcal{G}^0_I$.
<!-- ACF Have you checked if it is possible to state the difference between \label{eq-HGI0} and \label{eq-HGammaSAR}? At the end of the day, that is what we want to assess. -->
<!-- Corrected -->
```{r fig-convergence, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="45%",  fig.pos="hbt", fig.cap="$H_{\\lambda}(\\mathcal{G}^0_I)$ converges to the $H_{\\lambda}(\\Gamma_{\\text{SAR}})$ when $\\alpha\\to-\\infty$, with $L=8$ and $\\lambda=0.8$.", fig.width=4.5, fig.height=3.5}

@@

We found that the optimal value for $L > 1$ is $\lambda = 0.9$, as it minimizes the MSE while maintaining a low bias.
However, for $L = 1$, the optimal $\lambda$ tends to be higher, and we chose $\lambda = 3$ to achieve good results. 
@fig-optimal_order illustrates the case for $L = 5$.
```{r fig-optimal_order, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="42%",  fig.pos="hbt", fig.cap="Bias and MSE as a function of $\\lambda$, with $n=49$, $L=5$.", fig.width=7, fig.height=4.5}

@@

A Monte Carlo study with $1000$ replications for each sample size $n \in \{9, 25, 49, 81, 121\}$ from the $\Gamma_{\text{SAR}}$ ($\mu=1, L=5$) confirms that for $\lambda=0.9$, the bootstrap-corrected estimator $\widetilde{H}_{\lambda}$ ($B=200$) reduces both bias and MSE compared to the original $\widehat{H}_{\lambda}$, with significant improvements for small sample sizes, as shown in&nbsp;@fig-bias_mse.

@@

```{r fig-bias_mse, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="42%", fig.pos="hbt",  fig.cap="Bias and MSE of the Rényi entropy estimators for $\\Gamma_{\\text{SAR}}$.", fig.width=7, fig.height=5}

@@

Assume we have an estimator $\widetilde{H}_{\lambda}$ for the Rényi entropy of an arbitrary model. For testing&nbsp;\eqref{eq:hypothesis_test}, this estimator is expected to be close to the theoretical expression given in Equation&nbsp;\eqref{eq-HGammaSAR}. 
Since $L\geq1$ is known, we define the test statistic as follows:
\begin{multline}
\label{eq-test}
S_{\widetilde{H}_{\lambda}}(\bm{Z}; L) = \widetilde{H}_{\lambda} - \bigl\{\ln \widehat{\mu} - \ln L + \frac{1}{1-\lambda}
\bigl[-\lambda\,\ln\Gamma(L) \\ 
+ \ln\Gamma\bigl(\lambda(L-1)+1\bigr)  
- \bigl(\lambda(L-1)+1\bigr)\,\ln\lambda
\bigr]\bigr\},
\end{multline}
where $\widehat{\mu}={n}^{-1}\sum_{i=1}^n Z_{i}$ is the sample mean.
This test statistic should be close to zero when the null hypothesis holds.
@fig-densities shows the empirical density of $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$, based on $10^4$ replications of the $\Gamma_{\text{SAR}}$ model for each sample size $n \in \{49,81, 121\}$ with $\lambda=0.9$ and $L \in \{5,18\}$.
<!-- ACF 10^4 replications of samples of size?   -->
<!-- Corrected -->
```{r Simulated_densityR, echo=FALSE, message=FALSE}
set.seed(1234567890, kind = "Mersenne-Twister")

@@

```{r fig-densities, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="47%", fig.pos="hbt",  fig.cap="Empirical densities of $S_{\\widetilde{H}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$.", fig.width=9, fig.height=4.0}

@@

The standardized test statistic 
$\varepsilon = ({S_{\widetilde{H}_{\lambda}}(\bm{Z}; L) - \hat{\mu}_S})/{\hat{\sigma}_S}$ is asymptotically standard normal distributed,
where $\hat{\mu}_S$ and $\hat{\sigma}_S$ are the empirical mean and standard deviation of $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$, obtained by Monte Carlo simulations under the null hypothesis. 
Thus, the $p$-values are calculated as $2\Phi(-|\varepsilon|)$,
where $\Phi(\cdot)$ is the cumulative distribution function of the standard normal distribution.
@fig-density_standardized shows smoothed histograms of standardized test statistics.

@@

```{r fig-density_standardized, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="35%", fig.pos="hbt", fig.cap="Standardized empirical densities of $S_{\\widetilde{H}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$.", fig.width=4, fig.height=2.5}

@@

The Rényi entropy-based test demonstrated greater sensitivity in detecting textural variations than the Shannon-based test due to the flexibility provided by the parameter $\lambda$, as observed in the binary maps in Figs.&nbsp;\ref{fig:london-c},&nbsp;\ref{fig:munich-c}, and&nbsp;\ref{fig:dublin-c}.
<!-- ACF Where is the Shannon-based approach shown? -->
<!-- JA: The results of the Shannon-based approach can be observed in the corresponding binary maps. -->

```{=latex}
\begin{figure*}[hbt]
    \centering
    \begin{subfigure}{0.17\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/london_2000.png}
        \caption{SAR image}
        \label{fig:london-a}
    \end{subfigure}
    \hspace{0.01\textwidth}
    \begin{subfigure}{0.20\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/p-values_renyi-london-E.png}
        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\lambda}}}$}
        \label{fig:london-b}
    \end{subfigure}
    \hspace{0.01\textwidth}
    \begin{subfigure}{0.17\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/H_005_london_renyi_L1_.png}
        \caption{Binary map for $\small{S_{\widetilde{H}_{\lambda}}}$}
        \label{fig:london-c}
    \end{subfigure}
    \hspace{0.01\textwidth}
    \begin{subfigure}{0.20\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/p-values_shannon-london-E.png}
        \caption{$p$-value map for $\tiny{S_{\widetilde{H}_{\text{AO}}}}$ }
        \label{fig:london-d}
    \end{subfigure}
    \hspace{0.01\textwidth}
    \begin{subfigure}{0.17\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/H_005_london_shannon.png}
        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
        \label{fig:london-e}
    \end{subfigure}
    \caption{Detection of heterogeneous areas in a SAR image over London, UK: comparison with the tests $\small{S_{\widetilde{H}_{\lambda}}}$ and $\small{S_{\widetilde{H}_{\text{AO}}}}$.}
    \label{fig:london}
\end{figure*}
```

```{=latex}
\begin{figure*}[hbt]
    \centering
    \begin{subfigure}{0.17\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/munich_1024.png}
        \caption{SAR image}
        \label{fig:munich-a}
    \end{subfigure}
    \hspace{0.01\textwidth}
    \begin{subfigure}{0.20\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/p-values_renyi_munich-H.png}
        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\lambda}}}$}
        \label{fig:munich-b}
    \end{subfigure}
    \hspace{0.01\textwidth}
    \begin{subfigure}{0.17\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/H_005_munich_renyi.png}
        \caption{Binary map for $\small{S_{\widetilde{H}_{\lambda}}}$}
        \label{fig:munich-c}
    \end{subfigure}
    \hspace{0.01\textwidth}
    \begin{subfigure}{0.20\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/p-values_shannon_munich-H.png}
        \caption{$p$-value map for $S_{\widetilde{H}_{\text{AO}}}$}
        \label{fig:munich-d}
    \end{subfigure}
    \hspace{0.01\textwidth}
    \begin{subfigure}{0.17\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/H_005_munich_shannon.png}
        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
        \label{fig:munich-e}
    \end{subfigure}
    \caption{Detection of heterogeneous areas in a SAR image over Munich, Germany: comparison with the tests $\small{S_{\widetilde{H}_{\lambda}}}$ and $\small{S_{\widetilde{H}_{\text{AO}}}}$.}
    \label{fig:munich}
\end{figure*}

@@

```{=latex}
\begin{figure*}[hbt]
    \centering
    \begin{subfigure}{0.17\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/dublin_1100.png}
        \caption{SAR image}
        \label{fig:dublin-a}
    \end{subfigure}
    \hspace{0.01\textwidth}
    \begin{subfigure}{0.20\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/p-values_renyi-dublin-B.png}
        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\lambda}}}$}
        \label{fig:dublin-b}
    \end{subfigure}
    \hspace{0.01\textwidth}
    \begin{subfigure}{0.17\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/H_005_dublin_renyi.png}
        \caption{Binary map for $\small{S_{\widetilde{H}_{\lambda}}}$}
        \label{fig:dublin-c}
    \end{subfigure}
    \hspace{0.01\textwidth}
    \begin{subfigure}{0.20\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/p-values_shannon-dublin-B.png}
        \caption{$p$-value map for $S_{\widetilde{H}_{\text{AO}}}$}
        \label{fig:dublin-d}
    \end{subfigure}
    \hspace{0.01\textwidth}
    \begin{subfigure}{0.17\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/H_005_dublin-shannon.png}
        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
        \label{fig:dublin-e}
    \end{subfigure}
   \caption{Detection of heterogeneous areas in a SAR image over Dublin Port, Ireland: comparison with the tests $\small{S_{\widetilde{H}_{\lambda}}}$ and $\small{S_{\widetilde{H}_{\text{AO}}}}$.}
